---
title: "Shiny app presentation"
author: "Redson"
date: "2023-10-27"
output: ioslides_presentation
---


```{r}
library(flexdashboard)
library(shiny)

```

## R Markdown

-Shiny is an open-source R package that enables building interactive web applications that can execute R code on the backend
-It provides an elegant and powerful web framework for building web applications using R

## A Shiny app

-  This is a Shiny app that takes as input a phrase (multiple words) in a text box input and outputs a prediction of the next word.
- This Shiny app with a text prediction model stands out due to its utilization of an advanced Natural Language Processing model that understands user input contextually. 
- It offers a user-friendly interface with adjustable parameters, allowing users to customize their experience.



## Input Code

```{r echo = TRUE}
# ui.R
shinyUI(fluidPage(
  titlePanel("Simple Shiny App"),
  sidebarLayout(
    sidebarPanel(
      numericInput("n", "Number of Points:", 50)
    ),
    mainPanel(
      plotOutput("plot")
    )
  )
))



```

## Server Code

```{r pressure}
library(shiny)
# server.R
shinyServer(function(input, output) {
  output$plot <- renderPlot({
    hist(runif(input$n))
  })
})

```

## Thank you
